SummaryStats

### 2023-05-11 analysis/code/exploration/Exploration.Rmd

```{r data import}
data <- read.csv("analysis/input/build.csv")

@@

ggsave("obs_yearly.png", device="png", path="analysis/output/exploration")
```

@@

plot_grid(yearly_plot, centuries_plot)
ggsave("terrs_yearly_cents.png", device="png", path="analysis/output/exploration")
```

@@

# plot side by side
plot_grid(size_time, size_time_no_outliers)
ggsave("terrsize_cents_boxplot.png", device="png", path="analysis/output/exploration")

@@

ggsave("cities_ext.png", device="png", path="analysis/output/exploration")
```

@@

plot_grid(TerrExtPlot(terrs, 1, "Lineage extinctions, yearly"), TerrExtPlot(terrs, 10, "10-year bins"),
          TerrExtPlot(terrs, 30, "30-year bins"), TerrExtPlot(terrs, 50, "50-year bins"))
ggsave("terrs_ext.png", device="png", path="analysis/output/exploration")

@@

plot_grid(size_ext, size_ext_no_outliers, ncol = 1)
ggsave("ext_max_size.png", device="png", path="analysis/output/exploration")

@@

ggsave("lifespan_histo.png", device="png", path="analysis/output/exploration")
```

@@

plot_grid(integ_50y, integ_1600_25y, integ_1800_10y,
          align="v", ncol=1)
ggsave("city_integ_boxplots.png", device="png", path="analysis/output/exploration")
```

>>>>

```{r data import}
data <- read.csv("analysis/input/build_full.csv")

@@

#ggsave("obs_yearly.png", device="png", path="analysis/output/exploration")
```

@@

plot_grid(yearly_plot, centuries_plot)
#ggsave("terrs_yearly_cents.png", device="png", path="analysis/output/exploration")
```

@@

# plot side by side
plot_grid(size_time, size_time_no_outliers)
#ggsave("terrsize_cents_boxplot.png", device="png", path="analysis/output/exploration")

@@

#ggsave("cities_ext.png", device="png", path="analysis/output/exploration")
```

@@

plot_grid(TerrExtPlot(terrs, 1, "Lineage extinctions, yearly"), TerrExtPlot(terrs, 10, "10-year bins"),
          TerrExtPlot(terrs, 30, "30-year bins"), TerrExtPlot(terrs, 50, "50-year bins"))
#ggsave("terrs_ext.png", device="png", path="analysis/output/exploration")

@@

plot_grid(size_ext, size_ext_no_outliers, ncol = 1)
#ggsave("ext_max_size.png", device="png", path="analysis/output/exploration")

@@

#ggsave("lifespan_histo.png", device="png", path="analysis/output/exploration")
```

@@

plot_grid(integ_50y, integ_1600_25y, integ_1800_10y,
          align="v", ncol=1)
#ggsave("city_integ_boxplots.png", device="png", path="analysis/output/exploration")
```
